Data Preparation

### 2023-03-24 x_data-crunching.qmd
playing around with landing time estimation

@@

final_sfn <- final |> cast_latLon_to_sfnet()
# blend crossing in network
# c.f. https://luukvdmeer.github.io/sfnetworks/reference/st_network_blend.html
# blend points with a tolerance.
# tol = units::set_units(50, "m")
final_sfn <- final_sfn %>%
    sfnetworks::st_network_blend(my_thr |> select(REF, geometry)) #, tolerance = tol)

@@

>>>>

viz_check_vertical(final)
```

```{r}
source("~/RProjects/paper-2023-ICNS/R/identify_threshold_overhead.R")
source("~/RProjects/paper-2023-ICNS/R/add_bearing_to_target.R")

@@

# check if we have a threshold overflight
ovr_thr <- identify_threshold_overhead(final, my_thr)
if(nrow(ovr_thr) > 0){
  message("THRESHOLD")
  eldt  <- ovr_thr |> filter(DIST_THR == min(DIST_THR))
  final <- final |> mutate(MST_LABEL = "ALDT") 
}else{
  message("NEED TO WORK ON LANDING TIME")
}

@@

Lets' work this out.

```{r}
# we have identified an arrival trajectory
trj_arr <- arr_trjs |> filter(UID %in% "0200cb-0") |> 
#trj_arr <- arr_trjs |> filter(UID %in% c("00b1f9-0")) |> 
# trim payload and add sequence id
  select(UID, TIME, ICAO24, LAT, LON, ALT_B)  |> 
  rowid_to_column("NODE_ID") |> 
  mutate(MST = NA_character_)

ldg_rwy <- trj_arr |> assign_landing_runway(.arp = arp) |> 
  inner_join(rwys, by = "REF")
my_thr  <- ldg_rwy |> select(UID, REF, LAT, LON, COMMENT) |> 
  cast_latlon_to_pts(.drop_coord = FALSE)

# check if we have a threshold overflight
ovr_thr <- identify_threshold_overhead(trj_arr, my_thr)
if(nrow(ovr_thr) > 0){
  message("THRESHOLD")
  eldt    <- ovr_thr |> filter(DIST_THR == min(DIST_THR)) 
  trj_arr[eldt$NODE_ID,"MST"] <- "ALDT"
}else{
  message("NEED TO WORK ON LANDING TIME")
}
```

look at function ahead ... started adding threshold --> complement/fill columns & calc landing time

```{r}
viz_check_vertical(trj_arr)
```
